Corporate Security Solutions for BYOD:\\ A Novel User-Centric and Self-Adaptive System

### 2015-06-26 MUSES_vs_BYOD_solutions.tex
a proposal
another proposal
a doubt about the 3 EC methods
Added taxonomy in Section 3 for issue #41 . Please @unintendedbear @amorag and @JJ check if I am not saying something weird

@@

On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods. These methods can be used for inference and optimisation, and they use different data as part of the process, such as:

@@

This being said, and because the refinement of rules is considered of the same importance as inferring new ones, the approaches that have been implemented are:

@@

\item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions. Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance.
The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.

@@

>>>>

As these tools have several different access levels and different detection methods. Therefore, we propose the next taxonomy in order to classify the BYOD methods described in this paper.

\begin{itemize}
\item {\em Online or offline threat detection method}. Tools can identify security threats during runtime (online) or before their implantation (offline). For example, using some kind of Data Mining technique, such as classification methods, or merely the system administrator experience, can be used to generate rules before the deployment of the tool (offline) to detect threats in runtime. However, new rules can not be added. On the contrary, a real-time adaptation using actual data sources, that modify the parameters of the detection system follows an online scheme.
\item {\em Updatable of fixed information database}. This classification is related with the previous one. The new information gathered by the system during runtime can be stored in a database to generate new rules. If this database is not changed during runtime, as in the offline example explained above, the database is {\em fixed}. An example could be the hand-coded rules of a firewall, such as {\em iptables}, obtained from an offline method. On the other hand, an updatable database, such as the system logs, that can be used to extract new information, may offer more valuable source for dynamic adaptation mechanisms. However, it is not mandatory for an online threat detection method to use a updatable database, as all the current data may be analysed and deleted once a new rule are created. 
\item {\em Invasive or non-invasive data access}. A system can be considered {\em invasive} if a user needs to use the tool to perform his job. For example, open a specific browser provided by the tool, instead the original device browser, such as Chrome of Safari. A {\em non-invasive} data access is transparent to the user. An example is a log analyser daemon that updates other programs configuration or send information to the company server.
\item {\em Superuser or non-superuser system control}. Using a tool in superuser mode would add more information and control than a non-superuser execution, as it can access to elements of the device usually forbidden for regular applications, such as network, logs or other devices. However using superuser control may lead to a lack of privacy for the user.
\end{itemize}

@@

On the other hand, the refinement or adaptation of the security rules is performed by the \textit{Knowledge Compiler} module, and it uses three EC methods. These methods can be used for inference and optimisation, and they use different data as part of the process, such as:
% [Pedro] maybe we should specify how the following data is used in each one of the 3 EC methods...

@@

This being said, and because the refinement of rules is considered of the same importance as inferring new ones, the approaches that have been implemented are:
% [Pedro] I'd change this to: "As the rule refinement process is considered of the same importance as inferring new ones, the following three approaches have been implemented:"
% or even to:
% "Due to the importance of the refinement process (it is considered of the same importance as inferring new ones) the following three approaches have been implemented:"

@@

\item A \textit{GP rule refinement} approach, which optimises the current set of rules, adjusting the values in the conditions. Thus, some superfluous parts of the rules and even complete rules could be removed or improved, obtaining for instance specialisations or generalisations of existing rules which could mean a better performance. % [Pedro] change "could mean a better" to "could lead to a better"
The evaluation of the whole set of security rules is done by considering the number of unlabelled patterns that are `covered' after the adjustments.

@@

% [Pedro] it is not clear for me whether those 3 methods can be used (are used) independiently or one after the other(s).
